		%\begin{abstract}
		\begin{center}
			\begin{adjustwidth}{1cm}{1cm} % عرض کمتر از متن اصلی
				\noindent
				{\FancyAbstractTitle{A}{\hspace*{-.8mm}}\fontsize{6pt}{1pt}\selectfont{BSTRACT.}}\quad
				\footnotesize
				%{\fontsize{8pt}{1pt}\selectfont
			We consider an elliptic partial differential equation in non-divergence form with a random diffusion matrix and random forcing term.
			To address this, we propose a mixed-type continuous finite element discretization in the physical domain, combined with a collocation discretization in the stochastic domain.
			For the mixed formulation, we first introduce a stochastic cost functional at the continuous level. This formulation is then enhanced to incorporate the vanishing tangential trace constraint directly into a mesh-dependent cost functional, rather than enforcing it in the solution’s function space. In this context, we define a mesh-dependent norm and provide an error analysis based on this norm.
			We employ the collocation method by collocating the stochastic equation at the zeros of suitable tensor product orthogonal polynomials. This approach leads to a system of uncoupled deterministic problems, simplifying computation.
			Furthermore, we establish an a poriori error bound for the fully discrete approximation, detailing the convergence rates with respect to the discretization parameters. Finally, numerical results are presented to confirm and validate the theoretical findings.
		%}
		\end{adjustwidth}
	\end{center}
		%\end{abstract}
		
%		\begin{keywords}
%			elliptic PDEs with random data, non-divergence form, finite element method, stochastic collocation method, a priori error estimate
%		\end{keywords}
%		
%		\begin{MSCcodes}
%			65C20, 65N30, 65N35, 65N15
%		\end{MSCcodes}
